---
title: "Data-Visualization-with-R-Basic"
author: "Rahadian Arthapati"
date: "10/25/2017"
output: html_document
---
```{r}
library(MASS)
library(ggplot2)
library(corrplot)
library(rpart)
library(aplpack) #Bagplot
```
## Showing more complex relationships between variables
# Correlation Plot
```{r}
mtCor<-cor(mtcars)
corrplot(mtCor, method = "ellipse")
```
# Displaying Decision Tree Models
```{r}
treeModel<-rpart(mpg ~.,data=mtcars)
plot(treeModel)
text(treeModel,ex=1.6,col="red",xpd=T)
```

```{r}
boxplot(Cars93$Min.Price, Cars93$Max.Price)

bagplot(Cars93$Min.Price, Cars93$Max.Price, cex = 1.2)
# Add an equality reference line
abline(a = 0, b = 1, lty = 2)

```

```{r}
numericalVars<- UScereal[, sapply(UScereal, is.numeric)]
# Compute the correlation matrix for these variables
corrMat<-cor(numericalVars)
# Generate the correlation ellipse plot
corrplot(corrMat,method="ellipse")
```

```{r}
par(mfrow=c(1,2))
par(cex.main=0.8)
plot(whiteside$Temp, whiteside$Gas)
title("Gas vs Temp. scatterplot")
plot(whiteside$Insul)
title("Insul barplot")

```
The specific type values used here are:

"p" for "points"
"l" for "lines"
"o" for "overlaid" (i.e., lines overlaid with points)
"s" for "steps"
"n" for empty plot
```{r}
# Set up a 2-by-2 plot array
par(mfrow=c(2,2))
# Plot the Animals2 brain weight data as points
plot(Animals$brain,type="p")
# Add the title
title("points")
# Plot the brain weights with lines
plot(Animals$brain,type="l")
# Add the title
title("lines")
# Plot the brain weights as lines overlaid with points
plot(Animals$brain,type="o")
# Add the title
title("overlaid")
# Plot the brain weights as steps
plot(Animals$brain,type="s")
# Add the title
title("steps")
```

```{r}
# Create the numerical vector x
x <- seq(0, 10, length = 200)
# Compute the Gaussian density for x with mean 2 and standard deviation 0.2
gauss1 <- dnorm(x, mean = 2, sd = 0.2)
# Compute the Gaussian density with mean 4 and standard deviation 0.5
gauss2 <- dnorm(x, mean = 4, sd = 0.5)
# Plot the first Gaussian density
plot(x,gauss1,type="l",ylab="Gaussian probability density")
# Add lines for the second Gaussian density
lines(x,gauss2, lty=3, lwd=3, col="red")
```

```{r}
# Plot MPG.city vs. Horsepower as open circles
plot(Cars93$Horsepower, Cars93$MPG.city,pch=1,ylab = "Miles per Gas",xlab = "Horse Power",cex=0.6)

# Create index3, pointing to 3-cylinder cars
index3<-which(Cars93$Cylinders==3)
m<-which(Cars93$Horsepower==max(Cars93$Horsepower))
# Highlight 3-cylinder cars as solid circles
points(Cars93$Horsepower[index3],Cars93$MPG.city[index3],pch=16, col="blue")
#Highlight the highest hp car
points(Cars93$Horsepower[m],Cars93$MPG.city[m],pch=18, col="red",cex=1.2)

# Add car names, offset from points, with larger bold text
text(x = Cars93$Horsepower[index3], 
     y = Cars93$MPG.city[index3],
     labels = Cars93$Make[index3], adj = -0.1, cex=0.9,font=4)
text(x = Cars93$Horsepower[m], 
     y = Cars93$MPG.city[m],
     labels = Cars93$Make[m], adj = 1.1, cex=0.9,font=4,srt=-15)
legend(x="topright",pch = c(16,18),col=c("blue","red"),legend = c("3-Cylinder Cars","Highest HP Cars"))
```


```{r}
boxplot(formula=sugars~shelf,data=UScereal,axes=F)

# Add a default y-axis to the left of the boxplot
axis(side = 2)

# Add an x-axis below the plot, labelled 1, 2, and 3
axis(side = 1, at = c(1,2,3))

# Add a second x-axis above the plot
axis(side = 3, at = c(1,2,3),
     labels = c("floor", "middle", "top"))
```
Using multiple plots to give multiple views of a dataset
```{r}
library(MASS)
library(car) #for qqPlot
# Set up a two-by-two plot array
par(mfrow=c(2,2))

# Plot the raw duration data
plot(geyser$duration, main="Raw data")

# Plot the normalized histogram of the duration data
truehist(geyser$duration, main="Histogram")

# Plot the density of the duration data
plot(density(geyser$duration) ,main="Density")

# Construct the normal QQ-plot of the duration data
qqPlot(geyser$duration, main="QQ-plot")
```
Constructing and displaying layout matrices
```{r}
layoutMatrix <- matrix(
  c(
    1, 0,
    0, 2,
    3, 0
  ), 
  byrow = T, 
  nrow = 3
)
layout(layoutMatrix)
layout.show(3)
# Construct vectors indexB and indexA
indexB <- which(whiteside$Insul=="Before")
indexA <- which(whiteside$Insul=="After")

# Create plot 1 and add title
plot(whiteside$Temp[indexB], whiteside$Gas[indexB],
     ylim = c(0,8))
title("Before data only")

# Create plot 2 and add title
plot(whiteside$Temp, whiteside$Gas,
     ylim = c(0,8))
title("Complete dataset")
# Create plot 3 and add title
plot(whiteside$Temp[indexA], whiteside$Gas[indexA],
     ylim = c(0,8))
title("After data only")
```
Using the symbols() function to display relations between more than two variables
```{r}
# Call symbols() to create the default bubbleplot
symbols(Cars93$Horsepower, Cars93$MPG.city,
        circles = sqrt(Cars93$Price),
        inches = 0.1)
```
Saving plot results as files
```{r}
# Call png() with the name of the file we want to create
png("bubbleplot.png")

# Re-create the plot from the last exercise
symbols(Cars93$Horsepower, Cars93$MPG.city,
        circles = sqrt(Cars93$Price),
        inches = 0.1)

# Save our file and return to our interactive session
dev.off()

# Verify that we have created the file
list.files(pattern = "png")
```
Using color to enhance a bubbleplot
```{r}
# Iliinsky and Steele color name vector
IScolors <- c("red", "green", "yellow", "blue",
              "black", "white", "pink", "cyan",
              "gray", "orange", "brown", "purple")

# Create the `cylinderLevel` variable
cylinderLevels<-as.numeric(Cars93$Cylinders)

# Create the colored bubbleplot
symbols(Cars93$Horsepower, Cars93$MPG.city, 
        circles = cylinderLevels, inches = 0.2, 
        bg = IScolors[cylinderLevels])
```
The tabplot package and grid graphics
```{r}
# Load the insuranceData package
library(insuranceData)

# Use the data() function to load the dataCar data frame
data(dataCar)

# Load the tabplot package
suppressPackageStartupMessages(library(tabplot))

# Generate the default tableplot() display
tableplot(dataCar)
```
A lattice graphics example
```{r}
# Load the lattice package
library(lattice)

# Use xyplot() to construct the conditional scatterplot
xyplot(calories ~ sugars| shelf,UScereal)
```







