---
title: "Data-Wrangling-with-R-Basic"
author: "Rahadian Arthapati"
date: "10/23/2017"
output: html_document
---

We will use some libraries to simplify the process of data wrangling.
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
```

## Case Studies 1
```{r}
students<-read.csv("https://assets.datacamp.com/production/course_723/datasets/students_with_dates.csv",stringsAsFactors = F)
# remove first column
students<-students[,-1]
save(students, file="students.RData")
```
convert date to tbl_df for easier manipulation
```{r}
x<-c(1:3,5,7:24,31:32)
std<-tbl_df(students)%>%na.omit()%>%select(names(students[,x]))
glimpse(std)
```
convert char into factor and date manually
```{r}
f<-c(1:2,6,9:12,16:21)
std[,f]<-lapply(std[,f],factor)
std["dob"]<-as.Date(std[["dob"]])
#glimpse(std)
std%>% group_by(sex)%>%summarise(count=n())
ggplot(std,aes(sex),color=sex)+geom_bar()
```
filter the student whose absences greater than average
```{r}
(std_year<-std%>%separate(dob,into="year",sep="-",remove=F))
absences<-std_year%>%group_by(sex)%>%summarise(avg_absences=mean(absences))
ggplot(std_year,aes(x=year,y=absences,color=sex))+geom_point()+facet_wrap(~ sex)
```
join the table
```{r}
std_absences<-std_year%>%left_join(absences,by="sex")%>%filter(absences>ceiling(avg_absences))
#ggplot(std_absences,aes(x=internet,y=absences,color=internet))+geom_point()
boxplot(absences ~ internet,data=std_absences,xlab="Internet Usage",ylab="Absences")
```

## Case Studies 2

```{r}
load(url("https://assets.datacamp.com/production/course_1800/datasets/ucb_admit.RData"))
glimpse(ucb_admit)
```
Count number of male and female applicants admitted
```{r}
(ucb_counts <- ucb_admit %>% count(Gender, Admit) %>% spread(Admit, n) %>% mutate(Perc_Admit = Admitted / (Admitted + Rejected)))
```
Table of counts of admission status and gender for each department
```{r}
(admit_by_dept <- ucb_admit %>%count(Dept, Gender, Admit) %>%spread(Admit, n)%>% mutate(Perc_Admit = Admitted / (Admitted + Rejected)))
```
Simpson's Paradox, 
is a phenomenon in probability and statistics, in which a trend appears in different groups of data but disappears or reverses when these groups are combined.
The practical significance of Simpson's paradox surfaces in decision making situations where it poses the following dilemma: Which data should we consult in choosing an action, the aggregated or the partitioned?
- Overall: males more likely to be admitted
- Within Most Departements : females more likely
When controlling for departement, relationship between gender and admission status is reversed
Potential reason (?):
- Women tended to apply to competitive departements with low admission rates
- Men tended to apply to less competitive departements with high admission rates

## Case Studies 3 - Sampling Strategies
Simple Random Sample
Stratified Sample
Cluster Sample *
Multistage Sample *
* common in economic reason
```{r}
library(openintro)
data(county)
#remove DC
(county_noDC<-county%>%filter(state != "District of Columbia") %>% droplevels())
```
Simple Random Sample of 150 County
```{r}
county_srs<-county_noDC%>%sample_n(size=150)
glimpse(county_srs)
#SRS state distribution
(county_srs%>%group_by(state)%>%count())
```
Stratified Sample
```{r}
county_str<-county_noDC%>%group_by(state)%>%sample_n(size=3)
glimpse(county_str)
county_str%>%group_by(state)
```

```{r}
load(url("https://assets.datacamp.com/production/course_1800/datasets/evals.RData"))
glimpse(evals)
```

```{r}
cat_vars <- c("rank", "ethnicity", "gender", "language",
              "cls_level", "cls_profs", "cls_credits",
              "pic_outfit", "pic_color")
evals <- evals %>%mutate(cls_type = ifelse(cls_students >= 60, "large", 
                      ifelse(cls_students > 18, "midsize", "small")))

ggplot(evals, aes(x=bty_avg,y=score,color=cls_type)) +
  geom_point()
```
## Case Studies 4
```{r}
library(MASS)

# Plot Max.Price vs. Price as red triangles
plot(Cars93$Price,Cars93$Max.Price,
,pch=17,col="red")

# Add Min.Price vs. Price as blue circles
points(Cars93$Price,Cars93$Min.Price,pch=16,col="blue")

# Add an equality reference line with abline()
abline(a = 0, b = 1, lty = 2)
```

